TGI-spinal-power

### 2022-05-09 analysis/tgispine_lme_power.Rmd
adding model summary to code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
```

@@

# first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
model.cold <- lmer(rating ~ manipulation + condition + cold_location +
                     (1|ID) + (1|procedure), 
                   data = df_sum[df_sum$VAS == 'cold' ,])
summary(model.cold)
```
# View the coefficients for each person (should vary, due to random slope model)
```{r}
coef(model.cold)
```

Create a model with more data points per variable, to extract more power
```{r}
# First, let's try to add 30 observations per variable combination, which would mean N = 30
model.coldN <- extend(model.cold, within = 'manipulation+condition+cold_location', n=30)
summary(model.coldN)
# check that number of data points per variable does = 30
dat_model <- xtabs(~ manipulation + condition + cold_location, data=getData(model.coldN))
print(dat_model)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
library(broom)
library(brms)
library(modelsummary)
library(tibble)

set.seed(1234)  # Make everything reproducible

# Define the goodness-of-fit stats to include in modelsummary()
gof_stuff <- tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "N", 0,
  "r.squared", "R²", 3
)
```

@@

# first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
# first the simplest model
model.cold <- lmer(rating ~ manipulation + condition + cold_location +
                     (1|ID), 
                   data = df_sum[df_sum$VAS == 'cold' ,])
# then adding procedure as a fiexed effect
model.cold2 <- lmer(rating ~ manipulation + condition + cold_location +
                     (1|ID) + (1|procedure), 
                   data = df_sum[df_sum$VAS == 'cold' ,])
# then modelling slope of the subjects
model.cold3 <- lmer(rating ~ manipulation + condition + cold_location +
                     (1+manipulation|ID) + (1|procedure), 
                   data = df_sum[df_sum$VAS == 'cold' ,])

# summarise all 3 models
modelsummary(list(model.cold, model.cold2, model.cold3),
             gof_map = gof_stuff)
```
# View the coefficients for each person (should vary, due to random slope model)

# Run power analysis - to do this use the simplest model (model.cold)
# First, Create a model with more data points per variable, to extract more power
```{r}
# First, let's try to add 30 observations per variable combination, which would mean N = 30
model.coldN <- extend(model.cold, within = 'manipulation+condition+cold_location', n=30)
summary(model.coldN)
# check that number of data points per variable does = 30
dat_model <- xtabs(~ manipulation + condition + cold_location, data=getData(model.coldN))
print(dat_model)
```
